RADseq Works in Primates, Dammit.

### 2012-12-08 trunk/paper/paper.tex
Added library prep and sequencing to paper

@@

\paragraph{Library Preparation and Sequencing}
\begin{itemize}
	\item 6 animals, table with sources and other info
	\item Etter et al. 2011, though with modifications
	\item How we picked enzyme, PspXI. UCSC oligoMatch
	\item Adapter sequences. Barcodes with at least 3 mismatches. PE adapter
	\item What did it look like on BioA? Size? Concentration?
	\item Sequenced on Illumina MiSeq. 150PE
	\item NYU Langone Medical Center's Genome Technology Center (name right?)
	\item How much actually loaded?
	\item 30\% spike in with PhiX control DNA to control for low diversity library
\end{itemize}

>>>>

\usepackage{color}

@@

\paragraph{Library Preparation and Sequencing}

	Genomic DNA from 6 animals was digested with \emph{PspXI} (New England Biolabs) and used to create a multiplexed RAD tag library. Our library preparation method followed that of Etter et al, 2011 with the following modifications: the P1 adapter top\textcolor{red}{(?)} oligonucleotide was modified to have an overhang corresponding to the cut site of \emph{PspXI}, and a longer P2 adapter suitable for paired end sequencing was used (P2\_top: 5'-\textcolor{red}{SEQUENCEHERE}-3'; P2\_bottom: 5'-\textcolor{red}{SEQUENCEHERE}-3'). Individual-specific barcodes contained in the P1 adapter differed by at least \textcolor{red}{three} nucleotides. We chose \emph{PspXI} based on the results of \emph{in silico} digestion of the human, rhesus macaque, and baboon reference genomes using custom Perl scripts (\textcolor{red}{refs}). We sequenced the prepared library as one 150-cycle paired-end run of an Illumina MiSeq at the NYU Langone Medical Center's Genome Technology Center using a spike-in of 30\% PhiX DNA to control for low diversity in the library at the barcode and restriction sites. Sequences are available to download from the NCBI Short Read Archive (accession number \textcolor{red}{SRAXXXXXX.X}).

%\begin{itemize}
	%\item 6 animals, table with sources and other info
	%\item Etter et al. 2011, though with modifications
	%\item How we picked enzyme, PspXI. UCSC oligoMatch
	%\item Adapter sequences. Barcodes with at least 3 mismatches. PE adapter
	%\item What did it look like on BioA? Size? Concentration?
	%\item Sequenced on Illumina MiSeq. 150PE
	%\item NYU Langone Medical Center's Genome Technology Center (name right?)
	%\item How much actually loaded?
	%\item 30\% spike in with PhiX control DNA to control for low diversity library
%\end{itemize}
